% !TEX program = xelatex

% v1.0

\documentclass[]{allanwang-resume}
	\usepackage{fancyhdr}
    \pagestyle{fancy}
    \fancyhf{}
    \usepackage{tikz}
\begin{document}

\firstname{Allan}
\lastname{Wang}
\phone{(778) 968-5909}
\email{me@allanwang.ca}
\website{allanwang.ca/dev}
\github{AllanWang}
\header

\begin{minipage}[t][][b]{0.33\textwidth}~

	\resizebox{0.628\textwidth}{!}{
		\newcommand\logoheight{3.19}
		\begin{tikzpicture}[line width=2mm, line cap=round, draw opacity = 0.7]
			\draw (-1, 0) -- (-2, \logoheight);
			\draw (1, 0) -- (2, \logoheight);
			\draw [accent] (-1, 0) -- (0, \logoheight);
			\draw [accent] (1, 0) -- (0, \logoheight);
		\end{tikzpicture}
	}

	\vspace{0.26cm}

	\section{Education}
	\subsection{McGill University}
	\descript{BS in Software Engineering}
	\content{Sep 2015 | Montreal, QC}
	J.W. McConnell Scholarship \\
	Exp. Grad 12/18
	\sectionsep

	\section{Course Work}
	\subsection{Undergraduate}
	\content{Computer Science}
	Algorithms \& Data Structures \\
	Software Design \\
	Programming Lang \& Paradigms \\
	Operating Systems \\
	Theory of Computation \\
	Software Engineering Project \\
	\content{Mathematics}
	Linear Algebra \& Geometry \\
	Discrete Structures \\
	Calculus \\
	\sectionsep

	\section{Skills}
	\subsection{Programming}
	\content{Over 5000 lines}
	Java \tb Kotlin \tb Android \tb Git \tb HTML\\
	\content{Over 1000 lines}
	C \tb JavaScript \tb SCSS \tb Bash \tb \LaTeX\ \\
	\content{Familiar}
	Python \tb OCaml \tb PHP \\
	\sectionsep

	\section{Open Source}
	\subsection{Other Contributions}
	\content{github.com}
	AllanBot \tb VR PlayGround \tb \\
	SyMath \tb SwipeRecyclerView \tb \\
	sNNake-2.1 \tb IconShowcase \tb \\
	Capsule \tb Prime-Number-Calculator \tb \\
	matchr 

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

	\section{Projects}

	\project{Kotlin Android Utils}{Open Source}{Jun 2017 - Present}
	\vspace{\topsep} % Hacky fix for awkward extra vertical space
	\begin{tightemize}
		\item[] \stats[stars=31, forks=4]
		\item Created a large collection of \textbf{Android} extensions using Kotlin's DSL patterns to simplify common function calls.
		\item Implemented complex views with concise yet extensible interfaces.
		\item Created delegates for common UI patterns \& interfaces.
		\item Created pure \textbf{Kotlin} functions for concurrency handling \& lazy loading.
		\item Greatly facilitated code reuse, as KAU is downloaded \textasciitilde2k times per month through JitPack.
	\end{tightemize}

	\project{Frost for Facebook}{Open Source}{May 2017 - Present}
	\begin{tightemize}
		\item[] \stats[downloads=66500, stars=26, forks=10]
		\item Third party wrapper adding native features to Facebook's mobile site.
		\item Built upon \textbf{reactive} programming to deal with multithreaded loading.
		\item Created to enhance multitasking, performance, \& battery usage.
		\item Brought material design \& newer Android SDK standards to Facebook.
	\end{tightemize}

	\project{TEPID}{McGill Computer Taskforce}{Jun 2016 - Present}
	\begin{tightemize}
		\item Printing system used by over \textbf{6000} students at \textbf{McGill University}.
		\item Contributed to a \textbf{REST API} backed by \textbf{Jackson} \& \textbf{CouchDb}.
		\item Added \textbf{Gitlab CI} to greatly improve workflow efficiency.
		\item Modularized shared components to maximize code reuse, such as an API handler made with \textbf{Retrofit}.
		\item Wrote an \textbf{Android} counterpart to help manage the print jobs.
	\end{tightemize}

	\project{Artwork DIY}{Haiyi}{Jul 2017 - Nov 2017}
	\begin{tightemize}
		\item Lead an \textbf{Android} app for selling phone cases online.
		\item Created an interactive model using matrices to manipulate image sets.
		\item Integrated the app with \textbf{PayPal} and a \textbf{REST API}.
	\end{tightemize}

	\project{Material Glass}{Open Source}{Mar 2013 - Jun 2017}
	\begin{tightemize}
		\item[] \stats[downloads=662000, stars=9, forks=4]
		\item Created the \textbf{first} system theme for \textbf{Android Lollipop} using the Cyanogenmod Theme Engine.
		\item Greatly improved workflow by creating scripts and using CI \& CD.
	\end{tightemize}

	\sectionsep
	\section{Experience}

	\project{Server Admin}{Computer Taskforce}{Mar 2016 - Present}
	\begin{tightemize}
		\item Maintained \& improved printing \& web services for students at McGill.
		\item Manage VMs \& REST APIs used within the services.
		\item Focused on improving workflow through continuous deployment \& on code reuse by being an open source organization.
	\end{tightemize}

	\project{Tutor}{McGill Tutoring Service}{Sep 2016 - Present}
	\begin{tightemize}
		\item Tutored other students in Math \& CS.
		\item Created a website with notes for various classes.
		\item Moderated \& helped students in previously taken courses on Facebook on my own time.
	\end{tightemize}

\end{minipage}
\end{document}
