% !TEX program = xelatex

\documentclass[]{allanwang-resume}
	\usepackage{fancyhdr}
    \pagestyle{fancy}
    \fancyhf{}
    \usepackage{tikz}
\begin{document}
 
\firstname{Allan}
\lastname{Wang}
\phone{(415) 881-0867}
\email{me@allanwang.ca}
\website{allanwang.ca/dev}
\github{AllanWang} 
\header

\hspace*{-\parindent}%
\begin{minipage}[t][][b]{0.33\textwidth}~

	\resizebox{0.628\textwidth}{!}{
		\newcommand\logoheight{3.19}
		\begin{tikzpicture}[line width=2mm, line cap=round, draw opacity = 0.7]
			\draw (-1, 0) -- (-2, \logoheight);
			\draw (1, 0) -- (2, \logoheight);
			\draw [accent] (-1, 0) -- (0, \logoheight);
			\draw [accent] (1, 0) -- (0, \logoheight);
		\end{tikzpicture}
	}~\\

	% \vspace{0.26cm}

	\section{Education}
	\subsection{McGill University}
	\descript{BS in Software Engineering}
	\content{Sep 2015 | Montreal, QC}
	J.W. McConnell Scholarship \\
	Exp. Grad Jun 19
	\sectionsep

	\section{Course Work}
	\subsection{Undergraduate}
	\content{Computer Science}
	Algorithms \& Data Structures \\
	Software Design \\
	Programming Lang \& Paradigms \\
	Operating Systems \\
	Theory of Computation \\
	Software Engineering Project \\
	\content{Mathematics}
	Linear Algebra \& Geometry \\
	Discrete Structures \\
	Calculus \\
	\sectionsep

	\section{Skills}
	\subsection{Programming}
	\content{Proficient}
	Java \tb Kotlin \tb Android \tb Git \tb HTML \tb \LaTeX \\
	\content{Experienced}
	Python \tb C \tb JavaScript \tb TypeScript \tb React \tb SCSS \tb Bash \\
	\content{Familiar}
	OCaml \tb Elm \tb Go \tb PHP \\
	\sectionsep

	\section{Open Source}
	\subsection{Other Projects}
	\content{github.com}
	\pair{\mygithub{Discord-Bot}}{Discord Bot} \\
	\pair{\mygithub{sNNake-2.1}}{Kotlin Genetic NN} \\
	\pair{\mygithub{AllanBot-Public}[Allanbot]}{Messenger Bot w/ Node.js} \\
	\pair{\githublink{Harvard2017}{matchr}{matchr}}{Hack Harvard 2017} \\ 
	\pair{\mygithub{VR-McHacks-2017}[VR PlayGround]}{McHacks 2017} \\
	\pair{\mygithub{Capsule}}{Android UI Library} \\
	\pair{\mygithub{SwipeRecyclerView}}{View Library} \\
	\pair{\githublink{jahirfiquitiva}{IconShowcase}{IconShowcase}}{Icon Pack Library} \\

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

	\section{Experience}
	
	\project{UX Engineer III}{Google}{July 2019 - Present}
	\vspace{\topsep} % Hacky fix for awkward extra vertical space
	\begin{tightemize}
		\item Lead large scale UI component migrations to support new UX paradigms.
		\item Created libraries across Comms Apps to facilitate UX-Eng alignment.
		\item Contributed to the broader Google community with helper tools, code review, UX input, and Kotlin readability.
	\end{tightemize}

	\project{UX Engineer Intern}{Google}{May 2018 - Aug 2018}
	\begin{tightemize}
		\item Built various native Android prototypes for the Comms UX team to determine feasibility and build consensus on new product ideas.
		\item Supported a cafe study alongside UX researchers and interaction designers by building demo prototypes under tight deadlines.
		\item Created helper classes and worked with the engineering team to bring polished motion to production code.
	\end{tightemize}

	\project{Server Admin}{Computer Taskforce}{May 2017 - May 2018}
	\begin{tightemize}
		\item Maintained \& improved printing \& web services for students at McGill.
		\item Managed VMs \& REST APIs used within the services.
		\item Focused on improving workflow through continuous deployment \& on code reuse by being an open source organization.
	\end{tightemize}

	\project{Tutor}{McGill Tutoring Service}{May 2016 - Dec 2017}
	\begin{tightemize}
		\item Tutored other students in Math \& Computer Science.
		\item Created a website with public notes for various classes.
		\item Moderated \& helped students in previously taken courses on Facebook on my own time.
	\end{tightemize}

	\sectionsep
	\section{Projects}

	\project{\mygithub{KAU}[Kotlin Android Utils]}{Android Library}{Jun 2017 - Present}
	\begin{tightemize}
		\item Created a large collection of Android extensions using Kotlin's DSL patterns to simplify method calls.
		\item Implemented pure Kotlin functions for concurrent \& lazy loading.
		\item Created several highly extensible UI \& utility components through delegation patterns.
		\item Amassed 184 stars on GitHub.
	\end{tightemize}

	\project{\mygithub{Frost-for-Facebook}[Frost for Facebook]}{Web Wrapper}{May 2017 - Present}
	\begin{tightemize}
		\item Created web wrapper adding native features to Facebook's mobile site.
		\item Built upon reactive programming to deal with multithreaded loading.
		\item Brought material design \& newer Android SDK standards to Facebook.
		\item Amassed 572 stars on GitHub, and actively used through F-Droid.
	\end{tightemize}

	\project{TEPID}{Printing Service}{Jun 2016 - Present}
	\begin{tightemize}
		\item Contributed to a printing system used by over 6k students at McGill, consisting of a REST API, client, CouchDb database, \& webserver.
		\item Maximized code reuse by modularizing shared components, abstracting implementations, and delivering through gradle and JitPack.
		\item Wrote an Android counterpart to help manage the print jobs.
	\end{tightemize}	

\end{minipage}
\end{document}
